Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-05 WRITEUP/ms.tex
mm's comment on cbar instead of legend
Finished my main revisions

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations. We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
%
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs. In \flower, the typical MCC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies. MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs. We find that MCCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
%
Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.

@@

\begin{figure*}[hptb]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accreting phase;
    %
    {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
    \label{fig:SFH}
   }
\end{figure*}

@@

We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions from the combination of the three considered evolution stages. We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.}. of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
%
Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun,
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$. This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is dominated by bulk rotational motion, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way, though the MCCs are more massive.

@@

If constant column density (Larson's third relation) were truly a
fundamental property of molecular clouds,
and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at that
mass surface density $\Sigma$.
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of
molecular clouds in agreement with \citet{Heyer09a}.
Previous studies suggest that the observed mass-size relation of molecular clouds
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of
column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters.
%
That is, MCCs in the starburst phase are more susceptible to collapse, as expected. The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%

@@

\AP{let us recall to make the not about different molecular tracers also here}
We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold. That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds?

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways. As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher $n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
%
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ (see top panels of \Fig{alpha16-28}). At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
%
The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$. This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature are probably limited by the spatial resolution.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%
This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.

The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

We do not find any major quantitative differences (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.

@@

>>>>

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations.
We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') 
using an H$_2$ density-based clump finder. 
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
%
In \flower, the typical MCC mass and size are $10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, 
which are comparable to those found in nearby spirals and starburst galaxies. 
MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way),
similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs. We find that MCCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in 
clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc 
($\simeq$\,0$\farcs$01), which is 
within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
%mm2 [citation or derivation needed?]   ***********
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.

@@

\begin{figure*}[hptb]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}:
    projected stellar mass distribution during {\it (a)} an early
    accreting phase;  {\it (b)} a major starburst following a merger
    event; and {\it (c)} a relatively quiescent post-starburst
    phase.
\label{fig:SFH}}
\end{figure*}

@@

We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions
%mm2 considering all the evolutionary stages of \flower and dividing the sample in
%a low  ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm
%cut}$\eq18.96\,\cc, lower panels) density cuts 
      from the combination of the three considered evolution stages.
      We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc
      (top panels) and a high cut \footnote{The highest density
        threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to
        a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the
        densest structure. However, not all evolutionary stages
        considered have at least one MCC at this highest density
        threshold, so we consider MCCs identified with the second
        highest density threshold instead.}.
 of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
%
Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
identified as a single component at low $n_{\rm cut}$. This main disk
component
%mm2 occupy the top right   [left not right!]
          occupies the top left
corner of \Fig{stellarRatio16}, with a low gas mass fraction of
$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
dominated by bulk
%mm2 motions,
rotational motion,
as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the
velocity dispersions of most MCCs in the accreting phase of \flower
are dominated by turbulent motions, 
%mm2 . On the other hand, [the first hand is missing]
  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
%mm2 in the quiescent disk-like phase.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
virial parameter comparable to some of the molecular structures
observed in the Milky Way,
%mm2 but the former is
     though the MCCs are
     more massive.

@@

%mm2 [fiddled with tenses and plurals]
If constant column density (Larson's third relation) were truly a
fundamental property of molecular clouds,
% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
%mm2 (i.e., 
   and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, 
one would expect a single point in the $\sigma_{\rm
  gas}^2/R$--$\Sigma$ relation at
% mm a given gas
    that
mass surface density $\Sigma$. 
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of 
molecular clouds
%mm2 [maybe this is excessive, but if we are discussing the issue it
% seems worth citing.]
     in agreement with \citet{Heyer09a}.
Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

%Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
%\citep{Larson81a, McKee07a}.
%Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
%which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
%the mass-size relation is also known as the constant column density relation and has been
%proposed as a fundamental property of molecular clouds on different physical scales.
%
%By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
%\begin{equation}
%A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
%\end{equation}
%Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
%\begin{equation}\label{eqn:constantcolumndensity}
%M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
%\end{equation}
%where we adopt $\mu = 2.5$ as the mean molecular weight.
%
%We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
%Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
%Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
%Further discussions on the interpretation of this is provided in \Sec{MR}.
%%
%%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby 
ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

We investigate possible variations in the dynamics of the molecular structures of \flower 
by adopting different
%mm2 sets
    values
of $n_{\rm cut}$ % in identifying the MCCs
to test the robustness of our results against the choice of density threshold. 
That is, how sensitively are the structure properties, and thus, the 
results presented in \Sec{singless}, dependent on the choice of density thresholds?

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher 
$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
 since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ 
(see top panels of \Fig{alpha16-28}). 
At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
%
%For instance, the cluster of points found at the lowest density threshold, 
%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$, 
%MCCs identified at lower density in the outskirts of \flower
%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
%%
%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.

%
The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, 
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
However, the sizes of MCCs are almost a factor of two smaller. This
%mm2 likely suggest
    suggests 
that the sizes of \highz molecular gas structures reported in the literature
are
%mm2
   probably
limited by the spatial resolution. 
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion 
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%mm2
   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
   higher velocities likely being produced by Toomre instability driven radial inflow.

   The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs
%mm2 of \flower
are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

% different evolutionary stages
%mm2 [rearranged]
We do not find any major quantitative differences  (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.

%\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
%The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
%by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
%can be understood by acknowledging the fact that a given MCC in \flower
%does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
%our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
%predictions for CO line emission in the work presented by
%\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
%That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
%that the MCCs in our simulation have lower column densities than the
%star-forming cores observed in the Milky Way, which are
%observationally well-resolved within an MCC, and indeed, have
%sufficient column density to form CO.
%
%In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
%This makes sense from simply the fact that smaller MCCs have smaller masses.
%However, what does it mean for them to lie on the same locus?
%
%The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
%an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
%%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
%%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
%%If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds,
%%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
%%regions of massive \SF.
%%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
%%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
%%  point on that relationship, at the constant $\Sigma$ value.  }
%However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
%with a certain tracer (e.g., \citealt{Ballesteros11}).
%That is, it is solely a result of $\rho\propto M R^{-3}$.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$.
%% naturally display a linear relationship in $\log M - \log R$ plot.
%
%% the widespread in density for a given R.
%We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
%As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
%Following \citet{Ballesteros02a}'s argument, we expect the density
%of MCCs to be independent of the cloud size (since they are identified in 3D-space).
%On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
%we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$.
%As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
%
%\begin{figure}
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
%\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
%At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
%See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower.
%For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
%\label{fig:n}}
%\vspace{0.5em}
%\end{figure}

@@

% \AP{I think we should add a in-text comparison with the following \citet{grisdale:2017,grisdale:2018,grisdale:2019}, particularly the \citet{grisdale:2017}, similarly to what we have done for \citet{Behrendt16a}}
